---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  warning = F,
  message = F
)
```

# ggcalendar

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

Create grammar-of-graphics calendars.

ggcalendar introduces a new positional aesthetic: 'date'.  Specify the position of your geom using date, and let ggcalendar() and the geom_*_calendar() functions place your geom.  Under the hood, the compute_group functions finds the x and y position for the calendar date and panels are created based on the month. 


```{r}
library(ggcalendar)
library(ggplot2)
library(lubridate)
library(tidyverse)
```


``` r
# install.packages("devtools")
devtools::install_github("EvaMaeRey/ggcalendar")
```
## Example




```{r}
return_dates_month("2023-01") %>% 
  ggcalendar() + 
  aes(date = date) + 
  geom_point_calendar()

return_dates_month("2023-01") %>% 
ggcalendar() + 
  aes(date = date) +
  geom_text_calendar() # defaults to day of month in ggcalendar

return_dates_month("2023-01") %>% 
ggcalendar() + 
  aes(date = date) + 
  geom_text_calendar(label = "Day", # override default
                     size = 2)

return_dates_month("2023-01") %>% 
ggcalendar() + 
  aes(date = date) + 
  geom_text_calendar() + 
  geom_point_calendar(data = . %>% filter(wday(date) %in% 2:6),
                      alpha = .2,
                      size = 5,
                      color = "cadetblue") + 
  theme(panel.background = element_rect(fill = "beige"))

```

```{r example}

## basic example code

c("2022-03-19", "2022-04-09", "2022-05-07", "2022-06-11", "2022-07-16") %>% 
  tibble(date = . ) %>% 
  mutate(date = date %>% as_date) %>% 
  mutate(future = Sys.Date() < date) ->
events

return_dates_year(2022) %>% 
  ggcalendar() +
  aes(date = date) +
  geom_text_calendar() + 
  geom_point_calendar(data = events,
                      aes(color = future),
                      size = 8, 
                      alpha = .5) +
  labs(title = "nu2ggplot2X^2sion")


```



```{r example2}

## basic example code
ggcalendar::return_dates_month(month = "2022-07") %>% 
  head

ggcalendar::return_dates_interval(start_date = "2022-07-01", end_date = "2022-08-31") %>% 
  ggcalendar() +
  aes(date = date) +
  geom_text_calendar(size = 8) + 
  geom_point_calendar(data = . %>% filter(date == "2022-07-04"),
                      size = 8, 
                      alpha = .5) +
  geom_point_calendar(data = . %>% filter(date < Sys.Date()),
                      size = 10, shape = "x")
```

# NYC flights Example

> Airline on-time data for all flights departing NYC in 2013. Also includes useful 'metadata' on airlines, airports, weather, and planes.



Data inspiration:  https://twitter.com/rappa753/status/1545729747774308354 @rappa753

```{r}

# example 
nycflights13::flights %>% 
  ungroup() %>% 
  mutate(date = as.Date(time_hour)) %>% 
  filter(year(date) == 2013) %>% 
  count(date) %>% 
  ggcalendar() +
  aes(date = date) +
  geom_point_calendar(data = . %>% tibble(), aes(size = n, 
                          color = n), 
                      alpha = .7, show.legend = F) + 
  scale_color_viridis_c(option = "inferno", direction = 1) + 
  scale_size(range = c(3,8)) +
  geom_text_calendar(aes(label = n), size = 2) + 
  NULL
```


---


# Births example

```{r}
births <- "https://raw.githubusercontent.com/EvaMaeRey/tableau/9e91c2b5ee803bfef10d35646cf4ce6675b92b55/tidytuesday_data/2018-10-02-us_births_2000-2014.csv"

readr::read_csv(births) %>% 
  mutate(month = str_pad(month, 2, pad = "0"),
         date_of_month = str_pad(date_of_month, 2, pad = "0")) %>% 
  mutate(date = paste(year, month, date_of_month, sep = "-") %>% as_date()) %>% 
  filter(year == 2012) %>% 
  ggcalendar() + 
  aes(date = date) + 
  geom_point_calendar() +
  aes(size = births) +
  aes(color = births) +
  geom_text_calendar(aes(label = day(date)), color = "oldlace", size = 2) + 
  guides(
    colour = guide_legend("Births"),
    size = guide_legend("Births")
 ) + 
  geom_point_calendar(data = data.frame(date =
                                      as_date("2012-12-25")),
                      size = 5, color = "red", shape = 21)
  


```

---

# data defaults to calendar year and aes(date = date)

The following feels a little weird to me, but is allowed.  

A grammar of graphics fundamental is that a statistical graphic are composed of geometries/marks that take on aesthetics (color, position, size), to represent a variable.

Below we aren't aren't fully stating these specifications; which feels a bit funny; I would not recommend this as a starting point.  

```{r}
ggcalendar() + 
 geom_text_calendar()
```

Under the hood:

ggcalendar() 
  - has a data default of the current calendar year
  - has the date aes specified: aes(date = date)
  - geom_text_calendar, uses a compute group function the finds the calendar day as the label for the text layer.
---

# A little on the internals, the compute group function or thank you lubridate!


```{r}
compute_group_calendar_script <- readLines("./R/compute_group_calendar.R")
```

```{r count, code = compute_group_calendar_script}
```

```{r}
# compute function
return_dates_year(1999) %>%
head() %>%
compute_group_calendar()
```



## How used in geom_point_calendar... default aes

```{r}
geom_point_calendar_script <- readLines("./R/geom_point_calendar.R")
```


```{r count, code = geom_point_calendar_script}
```


